---
title: "SCC ICA1"
author: "Team Uno"
date: "1/28/2020"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
bank <- read.csv("bank.csv")
glimpse(bank)
```

```{r run regression, include=FALSE}
regression <- scatter.smooth(x=bank$balance, y=bank$age, main="Age ~ Balance")
print(regression)
```

```{r, include=FALSE}
sumplot <- lm(bank$balance ~ bank$age + bank$job + bank$marital + bank$education, data=bank)
summary(sumplot)$coefficient
```
```{r F-test by var test, include=FALSE}

agetest <- var.test(bank$balance,bank$age, data = bank)
jobtest <- var.test(bank$balance,bank$job, data = bank)
lovetest <- var.test(bank$balance,bank$marital, data = bank)
educationtest <- var.test(bank$balance,bank$education, data = bank)
housingtest <- var.test(bank$balance,bank$housing, data = bank)
loantest <- var.test(bank$balance,bank$loan, data = bank)
daytest <- var.test(bank$balance,bank$day, data = bank)
monthtest <- var.test(bank$balance,bank$month, data = bank)
durationtest <- var.test(bank$balance,bank$duration, data = bank)
cammpaigntest <- var.test(bank$balance,bank$campaign, data = bank)
ytest <- var.test(bank$balance,bank$y, data = bank)

# print individual vectors to get the F test
```

```{r, f test by anova, include=FALSE}
null_bank_model = lm(balance ~ 1, data = bank)
full_bank_model = lm(balance ~ age + job + marital + education + default + housing + loan + contact + day + month + duration + campaign + previous, data = bank)

full_bank_model = lm(balance ~ age + marital, data = bank)
anova(null_bank_model, full_bank_model)
```


```{r, include=FALSE}
ggplot(bank,aes(y=balance,x=age,color=marital))+geom_point()+stat_smooth(method="lm",se=FALSE)
```

```{r, include=FALSE}
ggplot(bank,aes(y=balance,x=day,color=marital))+geom_point()+stat_smooth(method="lm",se=FALSE)
```


```{r, include=FALSE}
ggplot(bank,aes(y=balance,x=duration,color=marital))+geom_point()+stat_smooth(method="lm",se=FALSE)
```

```{r, include=FALSE}
ggplot(bank,aes(y=balance,x=campaign,color=marital))+geom_point()+stat_smooth(method="lm",se=FALSE)

```
```{r, include=FALSE}
ggplot(bank,aes(y=balance,x=previous,color=marital))+geom_point()+stat_smooth(method="lm",se=FALSE)
```

# Conclusion

*The final model is a representation of the dataset bank. It excludes the y, month, loan, housing, education, job variables due to the F-test.These variables don't aid in our regression model. If the p-value of the variance test is over 0.05 then it is not significant. The variances of x and y are hypothetically equal. The above presesents a multiple linear regression that predicts the variable balance, keeping martial status as the color and only constant variable. For the most part, our regression inputs a weak positive correlation. Almost flatline correlation. *

# References:
1. https://cran.r-project.org/web/packages/ggiraphExtra/vignettes/ggPredict.html
2. http://www.sthda.com/english/wiki/f-test-compare-two-variances-in-r
3. The best notes ever by Professor Bushong (:
